Student performance, engagement and experience when teaching includes Kaggle-in-class data challenges

### 2021-01-06 paper-kaggle.Rmd
p-value for ST fixed

---
title: A study of student performance, engagement and experience when using Kaggle-in-class data challenges

@@

```{r permtest}
pdif <- NULL
for (i in 1:1000) {
  x <- scores %>% select(class, perf)
  x <- x %>% mutate(class = sample(class))
  pdif <- c(pdif,
            median(x$perf[x$class=="Yes"])-
                   median(x$perf[x$class=="No"]))
}
dif <- median(scores$perf[scores$class=="Yes"])-
       median(scores$perf[scores$class=="No"])
```

Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`. Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.

>>>>

---
title: Student performance, engagement and experience when teaching includes Kaggle-in-class data challenges

@@

```{r permtest}
pdif <- NULL
for (i in 1:1000) {
  x <- scores %>% select(class, perf)
  x <- x %>% mutate(class = sample(class))
  pdif <- c(pdif,
            median(x$perf[x$class=="Yes (ST-PG)"])-
                   median(x$perf[x$class=="No (ST-UG)"]))
}
dif <- median(scores$perf[scores$class=="Yes (ST-PG)"])-
       median(scores$perf[scores$class=="No (ST-UG)"])
```

Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes (ST-PG)"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No (ST-UG)"]), 2)`. Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.
